mlr3spatiotempcv: Spatiotemporal Resampling Methods for 'mlr3

### 2020-11-05 joss/joss.Rmd
use ranger learner, put more weight on the bias in non-spatial cv
cc @mllg

@@

```{r rr-nspcv}
library("mlr3")
library("mlr3spatiotempcv")
set.seed(42)

@@

learner = lrn("classif.rpart", maxdepth = 3, predict_type = "prob")
resampling_nsp = rsmp("repeated_cv", folds = 4, repeats = 2)
rr_nsp = resample(
  task = task, learner = learner,
  resampling = resampling_nsp
)

rr_nsp$aggregate(measures = msr("classif.ce"))
```

@@

```{r rr-spcv}
task = tsk("ecuador")

learner = lrn("classif.rpart", maxdepth = 3, predict_type = "prob")
resampling_sp = rsmp("repeated_spcv_coords", folds = 4, repeats = 2)
rr_sp = resample(
  task = task, learner = learner,
  resampling = resampling_sp
)

rr_sp$aggregate(measures = msr("classif.ce"))
```

Here, the classification tree learner is around 0.05 percentage points worse when using Spatial Cross-Validation (SpCV) compared to Non-Spatial Cross-Validation (NSpCV).
The magnitude of this difference is variable as it depends on the dataset, the magnitude of STAC and the learner itself.
For algorithms with a higher tendency of overfitting to the training set, the difference between the two methods will be larger.

>>>>

Rephrased in other words: the higher performance results in a non-spatial CV scenario should not be relied on or used for reporting.
The positive bias in these results is substantial and the actual performance of the model is nowhere near this result.
Results from a SptCV are not unbiased but more close in reflecting the actual performance of the learner on unknown datasets.

@@

```{r rr-nspcv}
library("mlr3")
library("mlr3spatiotempcv")
library("mlr3learners")
set.seed(42)

@@

learner = lrn("classif.ranger", predict_type = "prob")
resampling_nsp = rsmp("repeated_cv", folds = 4, repeats = 2)
rr_nsp = resample(
  task = task, learner = learner,
  resampling = resampling_nsp
)

rr_nsp$aggregate(measures = msr("classif.auc"))
```

@@

```{r rr-spcv}
resampling_sp = rsmp("repeated_spcv_coords", folds = 4, repeats = 2)
rr_sp = resample(
  task = task, learner = learner,
  resampling = resampling_sp
)

rr_sp$aggregate(measures = msr("classif.auc"))
```

Here, the the random forest learners is around 0.15 worse in AUC when using Spatial Cross-Validation (SpCV) compared to Non-Spatial Cross-Validation (NSpCV).
The magnitude of this difference is variable as it depends on the dataset, the magnitude of STAC and the learner itself.
Algorithms with a higher tendency of overfitting to the training set will have a large spread in such scenarios.
